A Streaming Algorithm for 2-Center with Outliers in High Dimensions

### 2015-05-02 paper.tex
small change
Invariants and query algorithm edited

\begin{figure}[t]
	\centering
	\includegraphics[width=13em]{figs/definition}
	\caption{An example of $2$-center with 6 outliers}
	\label{fig:definition}
\end{figure}

@@

\paragraph{The Algorithm}
We now describe our algorithm for handling the case  $\delta^* > \alpha r^*$.
At any time, our algorithm maintains a partition of $P$ into three disjoint subsets
$B_1$, $B_2$, and Buffer.
The first point $p_1$ is assumed, w.l.o.g, to be in $B_1^*$. 
(We have already assumed that $p_1$ is not outlier.)
The algorithm tries to partition points in such a way that 
at the end,
$B_1$ contains the whole $B_1^*$, and $B_2$ contains the whole $B_2^*$,
with possibly some outliers being contained in $B_1$ and $B_2$.
%Buffer has always size at most $z$.
The algorithm sets $c_1 = p_1$ as the fixed center of $B_1$,
and picks $c_2$ among the points processed so far as a candidate 
for being the center of $B_2$.
Moreover, the algorithm maintains two values $\delta$ and $r$,
where at any time, $\delta$ is a lower bound of $\delta^*$, 
and $r$ is an upper bound of $2r^*$ (under a specific condition). %(if $c_p \in B_2^*$).

@@

\begin{enumerate}
\item [(a)] $\delta < \delta^*$ %$\delta$ is a lower bound of $\delta^*$
\item [(b)] if $c_2$ is set, then
\begin{enumerate}
	\item[1.] $r \leq \delta/2$
	\item[2.] $B(c_p, \radius{c_p}) \subset B_2(c_2, r)$
\end{enumerate}
\item [(c)] $B_1 \cap B_2^* = \emptyset$
\item [(d)]  if $\cp \in B_2^*$, then 
	\begin{enumerate}
		\item [1.] $2r^* \le r$
		\item [2.] $B_2 \cap B_1^* = \emptyset$
		\item [3.] all points in $\Buffer$ are outliers
	\end{enumerate}

@@

Invariant (b1): 
When an appropriate candidate for $c_2$ is found, 
$c_2$ is set to that candidate by the main algorithm (Algorithm~\ref{alg:case-1}),
and $\rc$ is set to $\frac{2}{\alpha}\len{c_1c_2}$.
After that, points are added to $B_2$ by function \textproc{AddToB$_2$}
only if they are within $\rc$-radius of $c_2$.

If $c_2$ is set, then it is the $(z+1)$-furthest point from $c_1$ in a set $T \subset P$.
Let q be the $(z+1)$-furthest point from $c_1$ in the stream at that state, then $\len{c_1c_2} \leq \len{c_1q}$ and since (for $16 \leq \alpha$) $\radius{c_2} \leq \frac{1}{6}\frac{\alpha \len{c_1 q}}{(\alpha + 4)} \leq \delta / 6$, then 
$$r \leq (2 + \frac{2}{\alpha})\radius{c_2} \leq 3 \radius{c_2}  \leq \delta /2.$$

In part 2, if $|B_2| < \dz$ then $c_p = c_2$ and $r = \radius{c_2}$, so $B_2 = B(c_p, \radius{c_p})$. 
When the size of $B_2$ reaches $\dz$, the central point $\cp$ moves to the centerpoint of $B_2$ and $\rc$ increases by a factor of $(2 + \frac{2}{\alpha})$. 
Because the centerpoint of $B_2$ locate in $B_2$, then $c_p \in B(c_2, \radius{c_2})$.
So if $|B_2| \ge \dz$ then $\len{c_2 c_p} \leq \radius{c_2}$ and as a result
$$\radius{c_p} \leq \frac{2 (\len{c_1 c_2} + \len{c_2 c_p})}{\alpha} \leq \radius{c_2}(1 + \frac{2}{\alpha})$$ 
So $B(c_p, \radius{c_p}) \subset B_2(c_2, \radius{c_2}(2 + \frac{2}{\alpha}))$.

Invariant (c): A point $p$ can be added to $B_1$ in two parts of the \Cref{alg:case-1}. 
First case is in function \textproc{AddToB$_1$}, the point will be added to $B_1$ only if it is within distance $\delta$ of the center $c_1$,  when $\len{pc_1} \leq \delta$, which due to invariant (a), guaranties $\len{pc_1} < \delta^*$, so $p \not \in B_2^*$.

Second case is in \Cref{alg:case-1}, whenever the buffer overflows and $B_2$ is non-empty the algorithm takes one of the following actions depending on the size of $B_2$.
If $|B_2| < \dz $, then $c_2 = c_p$. \Cref{alg:case-1} add $c_2$ to $B_1$.
By contradiction assume that $c_p \in B_2^*$, then due to invariant (b) part 1 and invariant (d) part 1, $2r^* \leq r \leq \delta/2 < \delta^*/2$. So by Lemma \ref{lem:2r}, there should be at most $z$ points outside $B_1 \cup B_2$ which contradicts overflow of the buffer.

If $|B_2| \geq \dz$, then $c_p$ is the centerpoint of the first $\dz$ points currently in $B_2$. 
In this case, we add all points of $B_2$ to $B_1$. Due to invariant (b), $r \leq \delta/2 < \delta^*/2$. 
So By Lemma \ref{lem:center-point}, $c_p \in B_1^*$ or $c_p \in B_2^*$. By contradiction assume that $c_p \in B_2^*$. In this case, due to invariant (d) part 1 and invariant (b) part 2, $B_2$ covers $B(c_p, \radius{c_p})$ and $2r^* \leq r$. similar to previous part, it contradicts overflow of the buffer.

Invariant (d): 
Due to  Observation \ref{obs:c+4}, if $c_1 \in B_1^*$ and $c_p \in B_2^*$ then $1 \leq \frac{\len{c_1 c_p}}{\delta^*} \leq \frac{\len{c_1 c_p}}{\alpha r^*}$ and as a result $2r^* \leq \radius{c_p}$. If $|B_2| < \dz$ then $c_p = c_2$ and By \Cref{alg:case-1}, $r = \radius{c_2}$, so $2r^* \leq r$.

If $|B_2| \ge \dz$ then similar to invariant (b): $$2r^* \leq \radius{c_p} \leq (1 + \frac{2}{\alpha})\radius{c_2} \leq (2 + \frac{2}{\alpha})\radius{c_2} = r$$

In part 2, due to previous part, if $c_p \in B_2^*$ then $2r^* \leq r \leq \delta /2$ and $c_p \in B_2$. Due to invariant (a) and Observation \ref{obs:intersection}, $B_2$ intersect only with $B_2^*$ and so $B_2 \cap B_1^* = \emptyset$.

In part 3, due to invariant (c) and invariant (d) part 1, $2r^* \leq r \leq \delta/2 < \delta^* /2$. So by Lemma \ref{lem:2r}, all points outside $B_1 \cup B_2$ are outliers.

@@

\begin{proof}
Our data structures for maintaining $B_1$, $B_2$, and $B_u$
employ the streaming algorithm of~\cite{zarrabi2009streaming,chan2014streaming}
%To maintain an approximation to 1-center with $z$ outliers,
%we use the streaming algorithm of~\cite{zarrabi2009streaming}
%which combined with the %current best streaming algorithm for 1-center~\cite{chan2014streaming},
%result of~\cite{chan2014streaming},
which has an approximation factor of $1.22 \times \sqrt{2} <1.8$.
The algorithm of~\cite{zarrabi2009streaming}
uses $O(d^3z)$ space and $\poly(d,z)$ update time,
which implies the same bounds for \Cref{alg:case-1}.
Since we need to run $z + 1$ instances of \Cref{alg:case-1} in parallel, 
the space and update time is multiplied by a factor of $z$.
\end{proof}

@@

\end{tikzpicture}
\caption{State diagram for the KA algorithm.
Labels are taken from \cite{kim2014improved}.}
\label{fig:dag}
\end{figure}

@@

\noindent
As shown in \Cref{sec:estimate}, a desired estimate for $r$ can be
obtained by adding another level of 
parallelization that runs $O(1/\eps)$ instances of \Cref{alg:smallc} in parallel.

@@

%\newpage
\REM{
\section{Answering Queries}

At any point of the stream, we could be able to answer to a query (give the smallest $\alpha$-separated two congruent balls that covers all points except at most $z$ points).
Due to Invariants (c), we know that $B_1 \cap B_2^* = \emptyset$. 
So we are sure that, there exists a point $(B_2 \cup \Buffer) \cap B_2^* \neq \emptyset$.
In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.

\begin{lemma}
\label{lem:B2dz}
	At any point of the stream, 
	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
	then $B_2 \cap B_2^* = \emptyset$.
\end{lemma}

\begin{proof}
	due to invariant (b) part 1 and invariant (a) we know that $r \leq \delta/2 < \delta^*/2$. 
	By Lemma \ref{lem:center-point}, $c_p \in B_1^* \cap B_2^*$. 
	Since $c_p \not \in B_2^*$, then $c_p \in B_1^*$. 
	On the other hand, By Observation \ref{obs:intersection}, $B_2$ intersect with at most one of $B_1^*$ and $B_2^*$. So as a result, $B_2 \cap B_2^* = \emptyset$.
\end{proof}

As a result of Lemma \ref{lem:B2dz}, when $|B_2| \geq \dz$, we are sure that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
So if $|B_2| \ge \dz$, then our candidates $C$ for $c_2$ are $\{c_2\} \cup \Buffer$. Our Query algorithm, works as follows.

For each candidate $c \in C$, \Cref{alg:query} constructs $B'_1(c_1, \max \{\delta, \radius{c} \})$ and $B'_2(c, \radius{c})$. 
First, consider the candidate $c$ that equals to current $c_2$, then $B_1 = B'_1$. 
Since $\radius{c_2} \leq r \leq \delta/2$ (invariant (b) part 1) and $B'_2 \subset B_2$ then we don't need to construct any new set. 
In general case, when $c \neq c_2$, we know that $B_1 \subset B'_1$, so we just need to see which of $\Buffer \cap B_2$ points located in $B'_1$.
When $|B_2| \geq \dz$ and $c \neq c_2$, then it means that assumed $c_p \not \in B_2^*$. So By Lemma \ref{lem:B2dz}, $B_2$ can be added to $B'_1$ without contradicting invariant (c). 
So in this case, just need to see which points of $\Buffer$ should be added to $B'_1$. 
\Cref{alg:query} use functions \textproc{AddToB$'_1$} and \textproc{AddToB$'_2$} for adding a point to $B'_1$ and $B'_2$ respectively. 
Their definition are totally same as functions \textproc{AddToB$_1$} and \textproc{AddToB$_2$} except that, they add point to $B'_i$ instead of $B_i$($i = 1, 2$).

As \Cref{alg:query}, consider all valid cases of $c$, for one of $c \in C$, $c \in B_2^*$. 
Consider that $c$ as $c^*$ and corresponding $B'_1$ and $B'_2$ as $B''_1$ and $B''_2$. 
Since $1 \leq \frac{\len{c_1 c^*}}{\alpha^*} < \frac{\len {c_1 c^*}}{\alpha r^*}$(By Observation \ref{obs:c+4}) then $2r^* \leq \radius{c^*}$ and as a result $B^*_1 \subset B''_1$ and $B^*_2 \subset B''_2$ (By Lemma \ref{lem:2r}).
On the other hand, due to invariant (c) and distance of new points added to $B''_1$ compare to $B_1$ is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, so $B''_1 \cap B_2^* = \emptyset$.
As a result $B''_1$ and $B''_2$ totally covers $B_1^*$  and $B_2^*$ respectively, with some extra outlier points and remaining points in $\Buffer$ are certainly outliers.
The only unknown part is that \Cref{alg:query} does not know how many outliers are in $B''_1$ and $B''_2$.
So \Cref{alg:compute-min} tries all possible cases and choose the one with the minimum radius.

@@

}

@@

In this section, we describe how to obtain a value $r$,
such that $1.2r^* \le r < (1.2 + 2\eps/3)r^*$.
The following lemma provides the main ingredient.

@@

\begin{figure}[th]
	\centering
	\includegraphics[width=19em]{figs/2lt1}
	\caption{Proof of Lemma~\ref{lem:2-approx}}
	\label{fig:2lt1}
\end{figure}

@@

We use \Cref{alg:1-center} to find an estimate for $r$. 
Let $r_i$ be the radius calculated by \Cref{alg:1-center} after receiving
the $i$-th point, $p_i$.
Clearly, the sequence of $r_i$'s is increasing.
%We use a doubling strategy, similar o what is used in~\cite{zarrabi2008core}.
Let $k$ be an integer such that $2^{k-1} \le r_i \le 2^{k}$, and set $\ell_i = 2^{k}$.
%Let $l_1=r_1$ and $l_i=2^j l_1$, where $l_i$ is the smallest number satisfying $l_i \ge r_i$. 
Obviously, $\ell_i \le 2 r_i$,
and hence, by Corollary~\ref{cor:4-approx}, 
$\ell_i$ is a $(8 + 2\alpha)$-approximation to $r^*$.

@@

%When the first non-zero radius is observed, $l_1$ is set. 
We run $m$ instances of Algorithm~\ref{alg:smallc} for each value $r \in R_i$ in parallel. 
%for all the previous points, which have been stored in a buffer. It is not hard to see that the space complexity for storing these points is $\O(z)$. 
Whenever a new point $p_i$ is added, 
if $\ell_i=\ell_{i-1}$, then $R_i = R_{i-1}$,
and the new point is inserted to all parallel instances. %corresponding to candidates in $L_i$. 
%Otherwise, Algorithm~\ref{alg:smallc} should be executed for all of the candidates in $L_i$, with all the points. But this is not achievable due to space limitations. 
If $\ell_i > \ell_{i-1}$, then the set $R_i$ has two types of values.
Those values in $R_i$ which are less than $1.2\ell_i$ are also present in $L_{i-1}$,
because $t_i / t_{i-1}$ is a positive power of 2.
For these values, we continue executing the corresponding instance.
If a value $r \in R_i$ is not present in $R_{i-1}$, 
then we have $r \ge 1.2 \ell_{i - 1} \ge \ell_{i-1}$.
%To overcome this problem, note that if the candidate $x_j=j \times t_i \in L_i$ is also in $L_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued. If $x_j \notin L_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$). 
Since those points not lying in the candidate solution 
are saved in the buffer of Algorithm~\ref{alg:1-center} (which has size at most $z$), 
all non-outlier points of this algorithm lie in the candidate balls of Algorithm~\ref{alg:smallc}. 
These outliers have been stored in a buffer. 
Therefore, for a new value $r$, 
it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points in $B_1$.
%Overall, we get the following result.

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=13em]{figs/definition}
	\caption{An example of $2$-center with 6 outliers}
	\label{fig:definition}
	\vspace{-.5em}
\end{figure}

@@

\paragraph{The Algorithm}
We now describe our algorithm for handling the case  $\delta^* > \alpha r^*$.
At any time, our algorithm maintains a partition of $P$ into three disjoint subsets
$B_1$, $B_2$, and Buffer.
The first point $p_1$ is assumed, w.l.o.g, to be in $B_1^*$. 
(We have already assumed that $p_1$ is not outlier.)
The algorithm tries to partition points in such a way that 
at the end,
$B_1$ contains the whole $B_1^*$, and $B_2$ contains the whole $B_2^*$,
with possibly some outliers being contained in $B_1$ and $B_2$.
%Buffer has always size at most $z$.
The algorithm sets $c_1 = p_1$ as the fixed center of $B_1$,
and picks $c_2$ among the points processed so far as a candidate 
for being the center of $B_2$.
Moreover, the algorithm maintains two values $\delta$ and $r$,
where at any time, $\delta$ is a lower bound of $\delta^*$, 
and $r$ is an upper bound of $2r^*$ (under a certain condition). %(if $c_p \in B_2^*$).

@@

\begin{enumerate}
\item [(a)] $\delta < \delta^*$ %$\delta$ is a lower bound of $\delta^*$
\item [(b)] if $c_2$ is set, then
\begin{enumerate}
	\item[1.] $r \leq \delta/2$
	\item[2.] $B(c_p, \radius{c_p}) \subseteq B_2(c_2, r)$
\end{enumerate}
\item [(c)] $B_1 \cap B_2^* = \emptyset$
\item [(d)]  if $\cp \in B_2^*$, then 
	\begin{enumerate}
		\item [1.] $2r^* \le r$
		\item [2.] $B_2 \cap B_1^* = \emptyset$
		\item [3.] all points in $\Buffer$ are outliers
	\end{enumerate}

@@

Invariant (b1): 
%When an appropriate candidate for $c_2$ is found by Algorithm~\ref{alg:case-1}, 
%$c_2$ is set to that candidate point,
%and $\rc$ is set to $\frac{2}{\alpha}\len{c_1c_2}$.
%After that, points are added to $B_2$ by function \textproc{AddToB$_2$}
%only if they are within $\rc$-radius of $c_2$. 
When $c_2$ is set by Algorithm~\ref{alg:case-1}, 
it is the $(z+1)$-furthest point from $c_1$ in a set $T \subseteq P$,
and $\rc$ is set to $\frac{2}{\alpha}\len{c_1c_2}$.
Let $q$ be the $(z+1)$-furthest point from $c_1$ in the stream at that moment.
Then $\len{c_1c_2} \leq \len{c_1q}$.
Assuming $\alpha \ge 16$, we have 
$\radius{c_2} \leq \frac{1}{6}\frac{\alpha \len{c_1 q}}{(\alpha + 4)} \leq \delta / 6$, 
and hence,  
$$
	r \leq (2 + \frac{2}{\alpha})\radius{c_2} \leq 3 \times \radius{c_2}  \leq \delta /2,
$$
which means that after increasing $r$ by \textproc{AddToB$_2$},
the invariant still holds.

Invariant (b2): If $|B_2| < \dz$, then $c_p = c_2$ and $r = \radius{c_2}$, 
and hence, $B_2 = B(c_p, \radius{c_p})$. 
When the size of $B_2$ reaches $\dz$, 
the central point $\cp$ moves to the centerpoint of $B_2$,
and $\rc$ is increased by a factor of $(2 + \frac{2}{\alpha})$. 
Because the centerpoint of $B_2$ locates in $B_2$, then $c_p \in B(c_2, \radius{c_2})$.
Thus, if $|B_2| \ge \dz$ then $\len{c_2 c_p} \leq \radius{c_2}$, and hence
$$
	\radius{c_p} \leq \frac{2 (\len{c_1 c_2} + \len{c_2 c_p})}{\alpha} \leq \radius{c_2}(1 + \frac{2}{\alpha}).
$$ 
Therefore, $B(c_p, \radius{c_p}) \subseteq B_2(c_2, \radius{c_2}(2 + \frac{2}{\alpha}))$.

Invariant (c): A point $p$ can be added to $B_1$ in two cases. % by \Cref{alg:case-1}. 
The first case is in function \textproc{AddToB$_1$}, 
where the point is added to $B_1$ only if it is within distance $\delta$ of the center $c_1$,  
%when $\len{pc_1} \leq \delta$, 
which by invariant (a), 
guaranties $\len{pc_1} < \delta^*$. Therefore, $p \not \in B_2^*$ in this case.

The second case is in \Cref{alg:case-1}, when the buffer overflows and $B_2$ is non-empty.
The algorithm takes one of the following actions depending on the size of $B_2$.
If $|B_2| < \dz $, then $c_2 = c_p$. \Cref{alg:case-1} add $c_2$ to $B_1$.
By contradiction assume that $c_p \in B_2^*$, then due to invariants (b1) and (d1), 
$2r^* \leq r \leq \delta/2 < \delta^*/2$. 
Therefore, by Lemma \ref{lem:2r}, there must be at most $z$ points outside $B_1 \cup B_2$,
which contradicts the overflow of the buffer. 
If $|B_2| \geq \dz$, then $c_p$ is the centerpoint of the first $\dz$ points currently in $B_2$. 
In this case, we add all points of $B_2$ to $B_1$. 
By invariant (b), $r \leq \delta/2 < \delta^*/2$. 
Therefore, By Lemma \ref{lem:center-point}, $c_p \in B_1^*$ or $c_p \in B_2^*$. 
By contradiction, assume that $c_p \in B_2^*$. 
In this case, due to invariants (d1) and (b2), 
$B_2$ covers $B(c_p, \radius{c_p})$ and $2r^* \leq r$. 
Therefore, Similar to the previous part, it contradicts the overflow of the buffer.

Invariant (d1): 
By Observation \ref{obs:c+4}, if $c_1 \in B_1^*$ and $c_p \in B_2^*$,
then $1 \leq \frac{\len{c_1 c_p}}{\delta^*} \leq \frac{\len{c_1 c_p}}{\alpha r^*}$,
and as a result, $2r^* \leq \radius{c_p}$. 
If $|B_2| < \dz$, then $c_p = c_2$, and By \Cref{alg:case-1}, $r = \radius{c_2}$, hence, $2r^* \leq r$.
If $|B_2| \ge \dz$, then similar to invariant (b), 
$$
	2r^* \leq \radius{c_p} \leq (1 + \frac{2}{\alpha})\radius{c_2} \leq (2 + \frac{2}{\alpha})\radius{c_2} = r.
$$

Invariant (d2): By invariant (d1), if $c_p \in B_2^*$ then $2r^* \leq r \leq \delta /2$ and $c_p \in B_2$. 
Now, by invariant (a) and Observation~\ref{obs:intersection}, 
$B_2$ intersect only $B_2^*$, and hence, $B_2 \cap B_1^* = \emptyset$.

Invariant (d3): By invariants (c) and (d1), $2r^* \leq r \leq \delta/2 < \delta^* /2$. 
Therefore, by Lemma \ref{lem:2r}, all points outside $B_1 \cup B_2$ are outlier.

@@

\begin{proof}
Our data structures for maintaining $B_1$, $B_2$, and $B_u$
employ the streaming algorithm of~\cite{zarrabi2009streaming,chan2014streaming},
%To maintain an approximation to 1-center with $z$ outliers,
%we use the streaming algorithm of~\cite{zarrabi2009streaming}
%which combined with the %current best streaming algorithm for 1-center~\cite{chan2014streaming},
%result of~\cite{chan2014streaming},
which has an approximation factor of $1.22 \times \sqrt{2} <1.8$.
The algorithm of~\cite{zarrabi2009streaming}
uses $O(d^3z)$ space and $\poly(d,z)$ update time,
which implies the same bounds for \Cref{alg:case-1}.
Since we need to run $z + 1$ instances of \Cref{alg:case-1} in parallel, 
the space and update time is multiplied by a factor of $z$.
\end{proof}

@@

\end{tikzpicture}
\caption{State diagram of the KA algorithm.
Labels are taken from \cite{kim2014improved}.}
\label{fig:dag}
\end{figure}

@@

\noindent
As shown in \Cref{sec:estimate}, a desired estimate for $r$ can be
obtained by running $O(1/\eps)$ instances of \Cref{alg:smallc} in parallel.
Adding another level of parallelization to remove the assumption of $p_1$
being a non-outlier, we get the following.

@@

%---------------------------- Answering Queries ------------------------

\section{Answering Queries}

%Using \Cref{alg:case-1},
In the following, we show how to answer queries of this kind:
find two $\alpha$-separated congruent balls of minimum radius
to cover all but at most $z$ points of the stream processed so far.

Our query algorithm is presented in \Cref{alg:query}.
The idea behind the algorithm is as follows.
By our initial assumption about $p_1$ and by invariants (c), 
we know that $B_1$ completely contains $B_1^*$.
%because $B_1 \cap B_2^* = \emptyset$ . 
But for $B_2$, it might be the case that our assumption about $c_2$ 
was incorrect, and therefore, $B_2$ may not completely contain $B_2^*$. 
The overcome this, we try all possible candidates for $c_2$,
and compute, for each possible combinations of 
$B_1$, $B_2$, and Buffer, the best solution for 2-center with $z$ outliers
using function \textproc{ComputeMin} presented in \Cref{alg:compute-min}.

@@

Now, we show that the query algorithm correctly considers all possible candidates for $c_2$.
Let $C$ denotes the set of candidate points for $c_2$.
By invariants (c), we know that $B_1 \cap B_2^* = \emptyset$. 
Therefore, $(B_2 \cup \Buffer) \cap B_2^* \neq \emptyset$,
and hence, $C \subseteq (B_2 \cup \Buffer) \cap B_2^*$. % in general.
We now use the following lemma.
%In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.

\begin{lemma}
\label{lem:B2dz}
	At any time, 
	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
	then $B_2 \cap B_2^* = \emptyset$.
\end{lemma}

\begin{proof}
	By invariants (a) and (b1), we know that $r \leq \delta/2 < \delta^*/2$. 
	By Lemma~\ref{lem:center-point}, $c_p \in B_1^* \cap B_2^*$. 
	Since $c_p \not \in B_2^*$, then $c_p \in B_1^*$. 
	On the other hand, by Observation~\ref{obs:intersection}, 
	$B_2$ intersect at most one of $B_1^*$ and $B_2^*$. 
	Therefore, $B_2 \cap B_2^* = \emptyset$.
\end{proof}

\noindent
By Lemma \ref{lem:B2dz}, when $|B_2| \geq \dz$, 
we known that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
Therefore, if $|B_2| \ge \dz$, then our candidates for $C$ are $\{c_2\} \cup \Buffer$.

Our query algorithm works as follows. 
For each candidate point $c \in C$, \Cref{alg:query} 
constructs $B'_1(c_1, \max \{\delta, \radius{c} \})$ and $B'_2(c, \radius{c})$. 
If the candidate $c$ equals to current $c_2$, then, $B_1 = B'_1$. 
Since $\radius{c_2} \leq r \leq \delta/2$ by invariant (b1) and $B'_2 \subset B_2$,
we do not need to construct any new set. 
For $c \neq c_2$, we know that $B_1 \subset B'_1$, and hence,
we just need to see which points in $\Buffer \cap B_2$ are located in $B'_1$.
When $|B_2| \geq \dz$ and $c \neq c_2$, then it means that assumed $c_p \not \in B_2^*$. 
Therefore, by Lemma \ref{lem:B2dz}, $B_2$ can be added to $B'_1$ without contradicting invariant (c). 
So in this case, we just need to see which points of $\Buffer$ must be added to $B'_1$. 
\Cref{alg:query} use functions \textproc{AddToB$'_1$} and \textproc{AddToB$'_2$} for adding a point to $B'_1$ and $B'_2$ respectively. 
The definition of these functions are the same as \textproc{AddToB$_1$} and \textproc{AddToB$_2$},
except that, they add point to $B'_i$ instead of $B_i$ ($i = 1, 2$).

Since \Cref{alg:query} considers all valid candidates for $c$, 
at least for one $c^* \in C$, we have $c^* \in B_2^*$. 
We call the corresponding $B'_1$ and $B'_2$ by $B''_1$ and $B''_2$. 
Since by Observation \ref{obs:c+4},
$1 \leq \frac{\len{c_1 c^*}}{\alpha^*} < \frac{\len {c_1 c^*}}{\alpha r^*}$, 
we have $2r^* \leq \radius{c^*}$, and therefore,
$B^*_1 \subset B''_1$ and $B^*_2 \subset B''_2$ by Lemma~\ref{lem:2r}.
On the other hand, since the distance of the new points added to $B''_1$ compare to $B_1$ is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, 
we have by invariant (c) that  $B''_1 \cap B_2^* = \emptyset$.
As a result $B''_1$ (resp., $B''_2$) completely covers $B_1^*$  (resp., $B_2^*$), 
and points in $\Buffer$ are certainly outliers.
The only unknown part is that \Cref{alg:query} does not know how many outliers are in $B''_1$ and $B''_2$.
Therefore, \Cref{alg:compute-min} tries all possible cases and choose the one with the minimum radius.

@@

In this section, we show how to obtain a value $r$,
such that $1.2r^* \le r < (1.2 + 2\eps/3)r^*$.
The following lemma provides the main ingredient.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=19em]{figs/2lt1}
	\caption{Proof of Lemma~\ref{lem:2-approx}}
	\label{fig:2lt1}
\end{figure}

@@

We use \Cref{alg:1-center} to find an estimate for $r$. 
Let $r_i$ be the radius calculated by \Cref{alg:1-center} after receiving
the $i$-th point, $p_i$.
Clearly, the sequence of $r_i$'s is increasing.
%We use a doubling strategy, similar o what is used in~\cite{zarrabi2008core}.
Let $k$ be an integer such that $2^{k-1} \le r_i \le 2^{k}$, and set $\ell_i = 2^{k}$.
(If $r_i = 0$, we set $\ell_i = 0$.)
%Let $l_1=r_1$ and $l_i=2^j l_1$, where $l_i$ is the smallest number satisfying $l_i \ge r_i$. 
Obviously, $\ell_i \le 2 r_i$,
and hence, by Corollary~\ref{cor:4-approx}, 
$\ell_i$ is a $(8 + 2\alpha)$-approximation to $r^*$.

@@

%When the first non-zero radius is observed, $l_1$ is set. 
We run $m$ instances of Algorithm~\ref{alg:smallc} for each value $r \in R_i$ in parallel. 
%for all the previous points, which have been stored in a buffer. It is not hard to see that the space complexity for storing these points is $\O(z)$. 
Whenever a new point $p_i$ is added, 
if $\ell_i=\ell_{i-1}$, then $R_i = R_{i-1}$,
and the new point is inserted to all parallel instances. %corresponding to candidates in $L_i$. 
%Otherwise, Algorithm~\ref{alg:smallc} should be executed for all of the candidates in $L_i$, with all the points. But this is not achievable due to space limitations. 
If $\ell_i > \ell_{i-1}$, then the set $R_i$ has two types of values.
Those values in $R_i$ which are less than $1.2\ell_i$ are also present in $L_{i-1}$,
because $t_i / t_{i-1}$ is a positive power of 2.
For these values, we continue executing the corresponding instance.
If a value $r \in R_i$ is not present in $R_{i-1}$, 
then we have $r \ge 1.2 \ell_{i - 1} \ge \ell_{i-1}$.
%To overcome this problem, note that if the candidate $x_j=j \times t_i \in L_i$ is also in $L_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued. If $x_j \notin L_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$). 
Since those points not lying in the candidate solution 
are saved in the buffer of Algorithm~\ref{alg:1-center} (which has size at most $z$), 
all non-outlier points of this algorithm lie in the candidate balls of Algorithm~\ref{alg:smallc} which has center $p_1$ and radius at most $l_{i-1}$. 
These outliers have been stored in a buffer. 
Since Algorithm~\ref{alg:smallc} maintains two balls with radius at least $r$, 
one of which (say $B_1$) is centered at $p_1$, 
then all non-outlier points of Algorithm~\ref{alg:1-center} are in $B_1$,
and hence, they do not make any transition in the states of Algorithm~\ref{alg:smallc}.
Therefore, for any new value $r$, 
it suffices to execute Algorithm~\ref{alg:smallc} with only the 
outlier points in the buffer of Algorithm~\ref{alg:1-center}.
%Overall, we get the following result.
